\thetitle

### 2021-05-11 paper/paper.tex
minor

Therefore, in the future we plan to develop \ARA{} further to a actor-critic state-of-the-art
reinforcement learning algorithm. We hypothesise that due to the more correct state-action value
estimations of \ARA{} as compared to deep Q-Learning, cf. \citet{schneckenreither2020average}, the
critic will provide a better feedback of the value function update to the actor. This should lead to
better policies than with standard actor-critic algorithms, e.g. A3C~\citep{mnih2016asynchronous}.
%
Furthermore, one limitation of this proof-of-concept study is that due to the computational
complexity we restricted our scope to flow-shop production systems only. In subsequent studies we
plan to test the algorithms on job-shop queuing systems as well.
%
Additionally, we want to exploit hierarchical production
planning~\citep{schneeweibeta1995hierarchical} by implementing agents on different hierarchical
levels which can bargain with each other. For instance, one agent might be responsible for medium
term planning order release decision at the top level, while another agent concentrates on
short-term scheduling at the base level. At the start of the process a proposed order release plan
is generated by the first agent. Accordingly the agent from the base level performs a preliminary
scheduling of these orders and may report very expensive orders as feedback. This information is
then taken into consideration on the top level which adapts the order release plan accordingly. Here
the top level agent minimises the overall costs by load leveling on an aggregated model, while at
the bottom level the agent (mainly) minimises costs backorder costs.
%
Finally, although the introduced actions space reduction method, named \textit{independent agents},
works very well, it remains to be shown that the achievable policies are different to the ones for
agents without this adaption.

>>>>

Therefore, in the future we plan to develop \ARA{} further to a actor-critic state-of-the-art
reinforcement learning algorithm. We hypothesise that due to the more correct state-action value
estimations of \ARA{} as compared to deep Q-Learning, cf. \citet{schneckenreither2020average}, the
critic will provide a better feedback of the value function update to the actor. This should lead to
better policies than with standard actor-critic algorithms, e.g. A3C~\citep{mnih2016asynchronous}.
%
Furthermore, one limitation of this proof-of-concept study is that due to the computational
complexity we restricted our scope to flow-shop production systems only. In subsequent studies we
plan to test the algorithms on job-shop queuing systems as well.
%
Additionally, we want to exploit hierarchical production
planning~\citep{schneeweibeta1995hierarchical} by implementing agents on different hierarchical
levels which can bargain with each other. For instance, one agent might be responsible for medium
term planning order release decision at the top level, while another agent concentrates on
short-term scheduling at the base level. At the start of the process a proposed order release plan
is generated by the first agent. Accordingly the agent from the base level performs a preliminary
scheduling of these orders and may report very expensive orders as feedback. This information is
then taken into consideration on the top level which adapts the order release plan accordingly. Here
the top level agent minimises the overall costs by load leveling on an aggregated model, while at
the bottom level the agent (mainly) minimises backorder costs.
%
Finally, although the introduced actions space reduction method, named \textit{independent agents},
works very well, it remains to be shown that the achievable policies are different to the ones for
agents without this adaption.
